CUDA-accelerated Genetic Feedforward-ANN Training for Data Mining

### 2010-04-19 doc/abstract.tex
More updating of page 1 and 2
git-svn-id: http://svn.scesoc.ca/evolution/trunk@104 fee98b4c-d1c3-4d34-9525-a468159e4a48

% ----------------------------------------------------------------------------
\subsection{Genetic Algorithms} \label{ga}
% ----------------------------------------------------------------------------
Genetic algorithms (GAs) use multiple candidate solutions to simultaneously explore the search space of ANN parameters \cite{GA-ANN}. The "individuals" are randomly mutated, mated and selected during each of several generations. Mutation and mating is done using a problem-specific representation of candidate solutions and "genetic operators." Selection is performed by applying the classifier to the training set and calculating a fitness value (classifier accuracy). The competitive bias imposed by selection attempts to mimic the "survival of the fittest" principle so often seen in Nature.  Because GAs blindly search a solution space and ANNs can be of arbitrary complexity, this technique is suitable for data mining applications using large or complex data sets.

>>>>

% ----------------------------------------------------------------------------
\subsection{Genetic Algorithms as ANN Training Agents} \label{ga}
% ----------------------------------------------------------------------------
Genetic algorithms (GAs) use multiple candidate solutions to simultaneously explore the search space of ANN parameters \cite{GA-ANN}. The candidate ANNs are randomly mutated, mated and selected during each of several generations. Mutation and mating is done using a problem-specific representation of candidate solutions and "genetic operators." Selection requires calculating the fitness of each candidate ANN (a classifier accuracy metric such as sensitivity) then preferentially selecting candidate ANNs based on fitness. The competitive bias imposed by selection attempts to mimic the "survival of the fittest" principle so often seen in Nature.  Because GAs blindly search a solution space and ANNs can be of arbitrary complexity, this technique is suitable for data mining applications using large or complex data sets.
